### 2018-10-05 paper/paper.tex
lemma 1

Related literature \MS[t]{Cite!} argues that the lead time syndrome can only occur (i) if a lead
time is set dynamically and nonreciprocal according to the current \WIP{}-level and (ii) the order
releases monotonically depend on this lead time. In a practical point of view this assumption is
correct, however theoretically the interconnection between \WIP{}-level and number of releases is
not needed to infer this systematic releasing misbehavior.

\begin{proof}{Proof}
  Consider a manufacturer with constant demand and an order release mechanism which strictly
  increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
  the release decision does neither depend on the flow time nor lead time. However, considered over
  time this leads to a monotonically increasing \WIP{}-level which again leads to a monotonically
  increasing lead time.\qed
\end{proof}

@@

  % stddev(rel1) > stddev(rel0) -> stddev(dem1) > stddev(dem0)
  It is sensible to increase the standard deviation in the release pattern if the standard deviation
  in the demand increases.

@@

\begin{proof}{Proof by induction on the size of the deviations.}
  Wlog assume sufficient capacity for the single-stage manufacturer.
  % Base: stddev(rel1) > 0 -> stddev(dem1) > 0
  In case of a constant
  demand pattern, the only sensible release pattern is to release s.t. an over the time (nearly)
  constant output in the magnitude of the demand is achieved.
  % or the maximum achievable constant throughput.
  Any other release pattern will increase either back-orders or finished goods inventory and thus
  costs. Similarly the costs increase once variability in the demand is introduced, as possible
  unforeseen fluctuations in the demand require either to increase the stock level or accept
  back-order costs.
  %
  % IH: stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
  In case the demand deviation increases by any magnitude greater $0$, chances for the demand
  quantities further away from the mean are increased with probability $p>0$. Thus the planner has
  to decide whether to release additional quantity to be able to serve the demand which is more
  likely with probability $p$. Clearly, this increases chances for either inventory costs or
  back-order costs according to the decision of the planner and compared to the previous situation.
  \qed

@@

Put differently, for higher standard deviation in the demand higher fluctuations in the release
pattern are sensible. Thus, the scaled deviations in the demand specify a natural lower-bound of
release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span of the release decisions and \WIP{}-levels being
considered in the analysis. Recall that the standard deviation measures the expected deviation of
the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the \emph{time span considered} $\tsc(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \tsc(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval being considered. Thus under the
  assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule, $68.3\%$,
  $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$,
  and $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

>>>>

Related literature \MS[t]{Cite!} argues that the lead time syndrome can only occur (i) if a lead
time is set dynamically and nonreciprocal according to the current \WIP{}-level and (ii) the order
releases monotonically depend on this lead time. In a practical point of view this assumption is
correct, however theoretically the interconnection between \WIP{}-level and number of releases is
not needed to infer this systematic releasing misbehavior. The dynamic quoting of the lead time can
rather be seen as origin and perpetuating factor for the \LTS{} in practical situations.

\begin{lemma}
  The interconnection between \WIP{}-level (and also lead time for that sake), and the release
  pattern is not necessary to observe the systematic releasing misbehavior called lead time
  syndrome.
\end{lemma}

\begin{proof}{Proof}
  Consider a manufacturer with constant demand and an order release mechanism which strictly
  increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
  the release decision does neither depend on the flow time nor the lead time. However, considered
  over time this leads to a monotonically increasing \WIP{}-level which again leads to a
  monotonically increasing lead time. This cycle of larger \WIP{}, longer lead time, and increasing
  amount of released orders is commonly known as lead time syndrome. \qed
\end{proof}

@@

  % stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)

  Let $p \in \Nat$ be the periods. Suppose, the deviations of the mean demand are drawn by $\X_{0}$,
  $\X_{1}$ and the corresponding release pattern follow the random variables $\Lambda_{0}$ and
  $\Lambda_{1}$ respectively.
  % and the standard deviation $\stddev$ over a set of discrete
  Then, if $\stddev(\X_{1}) > \stddev(\X_{0})$  then $\stddev(\Lambda_{1}) > \stddev(\Lambda_{0})$
  is sensible.
  %
  Informally this means that for higher standard deviation in the demand a higher standard deviation
  in the release pattern is sensible.

  % It is sensible to increase the standard deviation in the release pattern if the standard
  % deviation in the demand increases.

@@

\begin{proof}{Proof by induction on the size of the deviations.}
  Wlog assume sufficient capacity for the single-stage manufacturer.
  % Base: stddev(dem1) > 0 -> stddev(rel1) > 0
  In case of a constant demand pattern, the only sensible release pattern is to release s.t. an over
  the time (nearly) constant output in the magnitude of the demand is achieved.
  % or the maximum achievable constant throughput.
  Any other release pattern will increase either back-orders or finished goods inventory and thus
  costs. Similarly the costs increase once variability in the demand is introduced, as possible
  unforeseen fluctuations in the demand require either to increase the stock level or accept
  back-order costs.
  %
  % IH: stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
  In case the demand deviation increases by any magnitude greater $0$, chances for the demand
  quantities further away from the mean are increased with probability $p>0$. Thus the planner has
  to decide whether to release additional quantity to be able to serve the demand which is more
  likely with probability $p$. Clearly, this increases chances for either inventory costs or
  back-order costs according to the decision of the planner and compared to the previous situation.
  \qed

@@

% The above lemma thus specifies that for higher standard deviation in the demand higher fluctuations
% in the release pattern are sensible.
Thus, the scaled deviations in the demand specify a natural
lower-bound of release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span of the release decisions and \WIP{}-levels being
considered in the analysis.
%
% Recall that the standard deviation measures the expected deviation of
% the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the \emph{time span considered} $\tsc{p}$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \tsc{p} \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
